Changes in accessibility to emergency and community food services during COVID-19 and implications for low income populations in Hamilton, Ontario

### 2021-09-02 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton.Rmd
R2-Created highlights file, made small edits requested by editorial office on submission
Created png version of figures and separate file for tables as requested by editorial team on submission of R2

@@

fb / fb_inset
```

@@

lih / p_lih
```

@@

acc_sensitivity
```

@@

los_pre / los_covid
```

@@

lc / lc_inset
```

@@

acc_pre / acc_covid
```

@@

acc_change / acc_change_inset
```

@@

```{r plot-local-i, echo=FALSE, fig.cap="\\label{fig:accessibility-changes-with-local-i}Changes in accessibility from pre-COVID-19 to during COVID-19. Highlighted areas had significantly large changes in accessibility according to Local Moran's I." }
ggplot() +
  geom_sf(data = accessibility_taz_change,
          aes(fill = acc_d,
              color = significance,
              alpha = significance),
          size = 1) +
  geom_sf(data = hamilton_boundary,
          fill = NA) +
  geom_sf(data = inset_box,
          linetype = "dotted",
          color = "red",
          fill = NA) +
  scale_fill_viridis_c(name = "Change in accessibility",
                       option =  "A", 
                       direction = 1,
                       breaks = c(-0.0008,
                                  -0.0006,
                                  -0.0004,
                                  -0.0002),
                       labels = c("-0.0008",
                                  "-0.0006",
                                  "-0.0004",
                                  "-0.0002")) +
  scale_color_manual(values = c("n.s." = "lightgray", 
                                "sig" = "black")) +
  scale_alpha_manual(values = c("n.s." = 0.5, 
                                "sig" = 1)) +
  guides(color = "none", 
         alpha = "none",
         fill = guide_legend(title.position = "top")) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "bottom")
```

>>>>

**Keywords**: Food insecurity; Emergency and community food services; Food banks; Accessibility; Balanced Floating Catchment Areas; COVID-19; Hamilton; Ontario; Reproducible research

\newpage

@@

fb / fb_inset

ggsave("./figures/figure-1.png")
```

@@

lih / p_lih

ggsave("./figures/figure-2.png")
```

@@

acc_sensitivity

ggsave("./figures/figure-3.png")
```

@@

los_pre / los_covid

ggsave("./figures/figure-4.png")
```

@@

lc / lc_inset

ggsave("./figures/figure-5.png")
```

@@

acc_pre / acc_covid

ggsave("./figures/figure-6.png")
```

@@

acc_change / acc_change_inset

ggsave("./figures/figure-7.png")
```

@@

```{r plot-local-i, echo=FALSE, fig.cap="\\label{fig:accessibility-changes-with-local-i}Changes in accessibility from pre-COVID-19 to during COVID-19. Highlighted areas had significantly large changes in accessibility according to Local Moran's I." }
ggplot() +
  geom_sf(data = accessibility_taz_change,
          aes(fill = acc_d,
              color = significance,
              alpha = significance),
          size = 1) +
  geom_sf(data = hamilton_boundary,
          fill = NA) +
  geom_sf(data = inset_box,
          linetype = "dotted",
          color = "red",
          fill = NA) +
  scale_fill_viridis_c(name = "Change in accessibility",
                       option =  "A", 
                       direction = 1,
                       breaks = c(-0.0008,
                                  -0.0006,
                                  -0.0004,
                                  -0.0002),
                       labels = c("-0.0008",
                                  "-0.0006",
                                  "-0.0004",
                                  "-0.0002")) +
  scale_color_manual(values = c("n.s." = "lightgray", 
                                "sig" = "black")) +
  scale_alpha_manual(values = c("n.s." = 0.5, 
                                "sig" = 1)) +
  guides(color = "none", 
         alpha = "none",
         fill = guide_legend(title.position = "top")) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        legend.position = "bottom")

ggsave("./figures/figure-8.png")
```
